method

### 2022-03-03 06_Paper/ER-ED/method.Rmd
accepted comment

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@Simmons2012].
The paradigm was written and presented using *Psychopy* [@Peirce2019].
We used *R* with *R Studio* [@RCore2021; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *BayesFactor*[@Morey2021] for all analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED.<!-- eventually perhaps refer to the _script and R Markdown file_ -->
A complete list of all measures assessed in the study can be found at OSF (<https://osf.io/vnj8x/>) and GitHub (https://github.com/ChScheffel/CERED).
<!-- Attention! OSF is still private -->

@@

The procedure described above was tested in a pilot study with $N=`r nrow(data_quest_pilot)`$ participants (`r length(which(data_quest_pilot$gender == 2))` female; age: $M = `r papaja::printnum(mean(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
<!-- direkt "above" wird das nicht beschrieben, die genaue procedure wird eigentlich auch erst unten beschrieben. Ich würde eher schreiben "The newly developed ER paradigm was tested in a pilot study" oder so ähnlich. --> 
Regarding self-reported arousal, results showed significant higher subjective arousal for active viewing of negative compared to neutral pictures.
<!-- Signifikanz beruht auf p-Werten? Würde ich angeben. --> 
However, ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
Regarding physiological responses, ER strategies were associated with reduced facial muscle activity of the *corrugator* and *levator* compared to active viewing of negative pictures.
In accordance with our previous study [@Scheffel2021], we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
<!-- kann man die Results irgendwo nachvollziehen? Ich würde zumindest MW, SD und p-Werte angeben wenn gesagt wird, dass es "signifikant" höher/nierdiger ist. Auch um zu zeigen, worauf sich die Aussage stützt. 
könnte man die Ergebnisse sogar in einer Tabelle/Abbildung darstellen? Je nachdem, wie wichtig die Pilotdaten für das Gesamt-Ms. sind...

>>>>

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@Simmons2012].
The paradigm was written and presented using *PsychoPy* [@Peirce2019].
We used *R* with *R Studio* [@RCore2021; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *BayesFactor*[@Morey2021] for all analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED.<!-- eventually perhaps refer to the _script and R Markdown file_ -->
A complete list of all measures assessed in the study can be found at OSF (<https://osf.io/vnj8x/>) and GitHub (https://github.com/ChScheffel/CERED).
<!-- Attention! OSF is still private -->

@@

The newly developed ER paradigm was tested in a pilot study with $N=`r nrow(data_quest_pilot)`$ participants (`r length(which(data_quest_pilot$gender == 2))` female; age: $M = `r papaja::printnum(mean(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
Regarding self-reported arousal, results showed significant higher subjective arousal for active viewing of negative compared to neutral pictures.
<!-- Signifikanz beruht auf p-Werten? Würde ich angeben. --> 
However, ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
Regarding physiological responses, ER strategies were associated with reduced facial muscle activity of the *corrugator* and *levator* compared to active viewing of negative pictures.
In accordance with our previous study [@Scheffel2021], we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
<!-- kann man die Results irgendwo nachvollziehen? Ich würde zumindest MW, SD und p-Werte angeben wenn gesagt wird, dass es "signifikant" höher/nierdiger ist. Auch um zu zeigen, worauf sich die Aussage stützt. 
könnte man die Ergebnisse sogar in einer Tabelle/Abbildung darstellen? Je nachdem, wie wichtig die Pilotdaten für das Gesamt-Ms. sind...
